\documentclass[aspectratio=169,10pt]{beamer}

% ── Packages ──────────────────────────────────────────────────────────────────
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{inconsolata}
\usepackage{booktabs}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{array}
\usepackage{colortbl}

% ── Color Palette ─────────────────────────────────────────────────────────────
\definecolor{Navy}{HTML}{0A2540}       % deep navy — primary brand
\definecolor{Gold}{HTML}{C49A19}       % gold — accent & decorative
\definecolor{PageBg}{HTML}{FAFAFA}     % near-white page background
\definecolor{TableHdr}{HTML}{EEF2F7}   % light blue-grey for table shading
\definecolor{RuleColor}{HTML}{CBD5E1}  % light border / rule color
\definecolor{BodyText}{HTML}{0A2540}   % dark navy body text
\definecolor{MutedText}{HTML}{6B7280}  % muted grey for secondary text
\definecolor{Success}{HTML}{059669}    % financial green
\definecolor{Danger}{HTML}{DC2626}     % financial red

% ── Theme Base ────────────────────────────────────────────────────────────────
\usetheme{default}
\setbeamertemplate{navigation symbols}{}
\setbeamercolor{background canvas}{bg=PageBg}
\setbeamercolor{normal text}{fg=BodyText}
\setbeamercolor{frametitle}{fg=white,bg=Navy}
\setbeamercolor{structure}{fg=Navy}
\setbeamercolor{alerted text}{fg=Danger}
\setbeamercolor{block title}{fg=white,bg=Navy}
\setbeamercolor{block body}{fg=BodyText,bg=TableHdr}

% ── Frame Title ───────────────────────────────────────────────────────────────
% Navy bar + gold underline. Uses beamercolorbox — no fragile TikZ overlay.
\setbeamertemplate{frametitle}{%
  \nointerlineskip
  \begin{beamercolorbox}[%
    wd=\paperwidth,ht=2.6ex,dp=1.0ex,%
    leftskip=1.2cm,rightskip=1.2cm]{frametitle}%
    \usebeamerfont{frametitle}\insertframetitle%
  \end{beamercolorbox}%
  \nointerlineskip
  {\color{Gold}\hrule height 1.5pt}%
}

% ── Footline ──────────────────────────────────────────────────────────────────
% Light separator rule + copyright / page number. No TikZ — reliable stacking.
\setbeamertemplate{footline}{%
  \nointerlineskip
  {\color{RuleColor}\hrule height 0.4pt}%
  \begin{beamercolorbox}[%
    wd=\paperwidth,ht=2.2ex,dp=0.8ex,%
    leftskip=0.8cm,rightskip=0.8cm]{normal text}%
    {\tiny\color{MutedText}\textcopyright{} Shannon Capital --- Confidential}%
    \hfill
    {\tiny\color{MutedText}\insertframenumber\,/\,\inserttotalframenumber}%
  \end{beamercolorbox}%
}

% ── Typography ────────────────────────────────────────────────────────────────
\setbeamerfont{frametitle}{size=\normalsize,series=\bfseries}
\setbeamerfont{title}{size=\LARGE,series=\bfseries}
\setbeamerfont{subtitle}{size=\small,series=\mdseries}
\setbeamersize{text margin left=1.2cm,text margin right=1.2cm}

% Paragraph spacing — Beamer defaults parskip to 0; restore readable breathing room
\setlength{\parskip}{0.45em}
\setlength{\parindent}{0pt}

% ── Metadata ──────────────────────────────────────────────────────────────────
\title{Shannon's Demon}
\subtitle{Monthly Performance Report --- May 2026}
\author{Shannon Capital}
\date{May 27, 2026, 8:07 PM BRT}
\institute{}

\begin{document}

\setbeamercolor{background canvas}{bg=Navy}
\begin{frame}[plain]
\begin{tikzpicture}[remember picture,overlay]
  \fill[Gold] (current page.north west) rectangle ([yshift=-0.18cm]current page.north east);
  \fill[Gold] (current page.south west) rectangle ([yshift=0.09cm]current page.south east);
\end{tikzpicture}
\vspace{2.0cm}
\begin{center}
  {\color{white}\fontsize{26}{32}\selectfont\bfseries Shannon's Demon}\\[0.4cm]
  {\color{Gold}\rule{7cm}{0.6pt}}\\[0.35cm]
  {\color{white!70!black}\normalsize\mdseries Monthly Performance Report}\\[0.15cm]
  {\color{Gold}\large\bfseries May 2026}\\[1.0cm]
  {\color{white!50!black}\small Shannon Capital}\\[0.1cm]
  {\color{white!35!black}\scriptsize Generated: May 27, 2026, 8:07 PM BRT}
\end{center}
\end{frame}
\setbeamercolor{background canvas}{bg=PageBg}

\begin{frame}{Executive Summary}
\vspace{0.4em}
{\small\color{BodyText}
This report covers a partial month with only 1 days of portfolio data, so figures should be interpreted with caution. The strategy recorded a return of +0.00\% over the available period, while SOL/BRL moved +0.00\% over the same window.

The portfolio returned +0.91\% less than CDI this month. In periods of low SOL volatility or directional moves, the strategy's risk premium over the risk-free rate can turn negative — this is a normal occurrence and expected to reverse over the full cycle. IBOV fell sharply this month, providing useful context: the SOL/BRL balanced portfolio behaved as an uncorrelated asset class relative to Brazilian equities, and outperformed IBOV.
}
\vspace{0.4em}
{\scriptsize\color{MutedText}\textit{See full commentary in the accompanying Markdown report.}}
\end{frame}

\begin{frame}{Month Performance: May 2026}
\vspace{0.3em}
\begin{center}
\arrayrulecolor{RuleColor}
\begin{tabular}{@{\hspace{0.5em}}l@{\hspace{2em}}r@{\hspace{0.5em}}}
\toprule
\rowcolor{Navy}\textcolor{white}{\textbf{Metric}} & \textcolor{white}{\textbf{Value}} \\
\midrule
Portfolio Return       & \textcolor{Success}{+0.00\%} \\
SOL/BRL Price Change   & \textcolor{Success}{+0.00\%} \\
CDI (month)            & \textcolor{Success}{+0.91\%} \\
IBOV (month)           & \textcolor{Danger}{-5.31\%} \\
Days with Data         & 1 \\
Rebalances             & 1 (1 buys, 0 sells) \\
Fees Paid              & R\$ 0,25 \\
Max Drawdown           & \textcolor{Danger}{$-$0.00\%} \\
Portfolio Start        & R\$ 100,00 \\
Portfolio End          & R\$ 100,00 \\
\bottomrule
\end{tabular}
\end{center}
\end{frame}

\begin{frame}{Rebalance History}
\vspace{0.3em}
\small
\begin{center}
\arrayrulecolor{RuleColor}
\begin{tabular}{@{\hspace{0.3em}}l l r r r r r@{\hspace{0.3em}}}
\toprule
\rowcolor{Navy}\textcolor{white}{\textbf{Date}} & \textcolor{white}{\textbf{Dir}} & \textcolor{white}{\textbf{Amount}} & \textcolor{white}{\textbf{Fill Price}} & \textcolor{white}{\textbf{Fee}} & \textcolor{white}{\textbf{P\&L}} & \textcolor{white}{\textbf{Drift}} \\
\midrule
2026-05-26 & \textcolor{Success}{Buy} & R\$ 50,00 & R\$ 422,44/SOL & R\$ 0,25 & {\color{MutedText}---} & {\color{Danger}50.00\%} \\
\bottomrule
\end{tabular}
\end{center}
\end{frame}

\begin{frame}{Benchmark Comparison (Since Inception)}
\vspace{0.3em}
\begin{center}
\arrayrulecolor{RuleColor}
\begin{tabular}{@{\hspace{0.5em}}l@{\hspace{2em}}r@{\hspace{2em}}r@{\hspace{0.5em}}}
\toprule
\rowcolor{Navy}\textcolor{white}{\textbf{Benchmark}} & \textcolor{white}{\textbf{This Month}} & \textcolor{white}{\textbf{Since Inception}} \\
\midrule
Shannon's Demon  & \textcolor{Success}{+0.00\%}   & \textcolor{Success}{+0.00\%}   \\
SOL Buy-and-Hold & \textcolor{Success}{+0.00\%}  & \textcolor{Success}{+0.00\%}  \\
CDI              & \textcolor{Success}{+0.91\%}  & \textcolor{Success}{+0.05\%}  \\
IBOV             & \textcolor{Danger}{-5.31\%} & \textcolor{Danger}{-0.48\%} \\
\bottomrule
\end{tabular}
\end{center}
\end{frame}

\begin{frame}{Tax Summary (Lei 9.250/1995 Art.~21)}
\vspace{0.3em}
\begin{center}
\arrayrulecolor{RuleColor}
\begin{tabular}{@{\hspace{0.5em}}l@{\hspace{2em}}r@{\hspace{0.5em}}}
\toprule
\rowcolor{Navy}\textcolor{white}{\textbf{Metric}} & \textcolor{white}{\textbf{Value}} \\
\midrule
Gross SELL Proceeds & R\$ 0,00 \\
Realized Gain       & \textcolor{Success}{R\$ 0,00} \\
Trades              & 0 \\
Status              & {\color{Success}Exempt (sales $\leq$ R\$35{,}000)} \\
Payment Deadline    & --- \\
\bottomrule
\end{tabular}
\end{center}
\end{frame}

\begin{frame}{Current Portfolio}
\vspace{0.3em}
\begin{center}
\arrayrulecolor{RuleColor}
\begin{tabular}{@{\hspace{0.5em}}l@{\hspace{2em}}r@{\hspace{2em}}r@{\hspace{0.5em}}}
\toprule
\rowcolor{Navy}\textcolor{white}{\textbf{Asset}} & \textcolor{white}{\textbf{Quantity}} & \textcolor{white}{\textbf{Value (BRL)}} \\
\midrule
SOL              & 0.118346 & R\$ 50,00 \\
BRL              & {\color{MutedText}---}              & R\$ 50,00 \\
\textbf{Total}  & {\color{MutedText}---}              & \textbf{R\$ 100,00} \\
\bottomrule
\end{tabular}
\end{center}
\vspace{0.6em}
\begin{tabular}{@{}ll}
  \textbf{Average Cost (AVCO):} & R\$ 422,44/SOL \\[0.2em]
  \textbf{Unrealized P\&L:}     & \textcolor{Success}{R\$ 0,01 (+0.02\%)} \\
\end{tabular}
\end{frame}

\begin{frame}{Cumulative Track Record}
\vspace{0.3em}
\begin{center}
\arrayrulecolor{RuleColor}
\begin{tabular}{@{\hspace{0.5em}}l@{\hspace{2em}}r@{\hspace{0.5em}}}
\toprule
\rowcolor{Navy}\textcolor{white}{\textbf{Metric}} & \textcolor{white}{\textbf{Value}} \\
\midrule
Since              & 2026-05-26 \\
Total Days         & 1 \\
Total Return       & \textcolor{Success}{+0.00\%} \\
CAGR               & \textcolor{Success}{+0.00\%} \\
Sharpe Ratio       & N/A \\
Max Drawdown       & \textcolor{Danger}{$-$0.00\%} \\
Total Rebalances   & 1 \\
Total Fees         & R\$ 0,25 \\
\bottomrule
\end{tabular}
\end{center}
\end{frame}

\begin{frame}[allowframebreaks]{Important Disclosures}
\scriptsize
\color{BodyText}
\setlength{\parskip}{0.5em}

\textcolor{Navy}{\textbf{NOT INVESTMENT ADVICE}} \quad
This material has been prepared by Shannon Capital for informational purposes
only. It does not constitute an offer, solicitation, or recommendation to buy
or sell any financial instrument or digital asset.

\textcolor{Navy}{\textbf{PAST PERFORMANCE}} \quad
Past performance does not guarantee future results. Returns shown are historical
and may not be representative of future performance.

\textcolor{Navy}{\textbf{RISK FACTORS}} \quad
This strategy involves investment in highly volatile digital assets. Risks
include: (i)~extreme price volatility and potential total loss of capital;
(ii)~liquidity risk --- positions may not be exitable at prevailing market
prices; (iii)~no guarantee of positive returns; (iv)~the strategy may
underperform a passive buy-and-hold position or risk-free rate (CDI) during
sustained directional markets; (v)~operational risks including exchange
downtime, API failures, and software errors.

\textcolor{Navy}{\textbf{REGULATORY}} \quad
This material has not been reviewed or approved by any regulatory authority
(CVM or otherwise). Shannon Capital is an independent asset manager. This
document does not constitute investment advice within the meaning of Lei
6.385/1976 or applicable CVM regulations. Recipients should obtain independent
financial, legal, and tax advice before making any investment decision.

\textcolor{Navy}{\textbf{TAX}} \quad
Tax information relating to Lei 9.250/1995 Art.~21 is provided for illustrative
purposes only and does not constitute tax advice. Recipients are solely
responsible for their own tax compliance obligations.

\vspace{0.3em}
{\color{MutedText}\textcopyright{} Shannon Capital. Confidential ---
Not for distribution. All rights reserved. Unauthorized reproduction or
redistribution is prohibited.}

\end{frame}

\end{document}
